### 2021-07-10 docs/manuscript/manuscript.tex
Update manuscript.tex

\subsection*{Methods}
In this study, we apply a Markov chain Monte Carlo (MCMC)-like algorithm to probe
the design space of three-node GRNs with the ability to generate a band-like
expression pattern (target phenotype) in the middle of an arrangement of 30
cells, which resemble a simple (1-D) morphogenetic field in a developing embryo.
Unlike most modeling studies published so far, here we explore the
space of GRN topologies with nodes having the potential to perceive differently
the same input signal. This allows for a lot more flexibility during the search
space process, and thus enables us to identify a larger set of potentially
interesting and realizable morphogen interpretation mechanisms.

>>>>

\subsection*{Methods}
In this study, we apply a Markov chain Monte Carlo (MCMC)-like algorithm to probe
the design space of three-node GRNs with the ability to generate a band-like
expression pattern (target phenotype) in the middle of an arrangement of 30
cells, which resemble a simple (1-D) morphogenetic field in a developing embryo.
Unlike most modeling studies published so far, here we explore the
space of GRN topologies with nodes having the potential to perceive
the same input signal differently. This allows for a lot more flexibility during the search
space process, and thus enables us to identify a larger set of potentially
interesting and realizable morphogen interpretation mechanisms.
